\documentclass[12pt]{article}
\usepackage[top=0.71in,bottom=0.781in,left=0.81in,right=0.81in%,a4paper
]{geometry}
\usepackage{natbib}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage[colorlinks,linkcolor=blue,citecolor=black]{hyperref}
\usepackage{caption}
\usepackage{subfigure}
\usepackage{pdfpages}
\usepackage{amsfonts,amsthm,amssymb,amsmath}
\usepackage{float}
\usepackage{natbib}
\usepackage{multirow}
\usepackage{indentfirst} %??????
\usepackage{booktabs}%????
\usepackage{ulem}
\linespread{1.5}
\setlength{\parskip}{3.6pt}




\title{Cover Letter}
%\author{Yunshen Yang,~Gongbing Bi,~Lindong Liu}
\date{}


\begin{document}
\maketitle
~\\
Dear Editors:


We would like to submit the enclosed manuscript entitled ``Lagrangian Heuristic for Simultaneous Subsidization and Penalization: Implementations on Rooted Travelling Salesman Games", which we wish to be considered for publication in ``Computer \& Operations Research". 

No conflict of interest exits in the submission of this manuscript, and manuscript is approved by all authors for publication. I would like to declare on behalf of my co-authors that the work described was original research that has not been published previously, and not under consideration for publication elsewhere, in whole or in part. All the authors listed have approved the manuscript that is enclosed.

In this work, we studied the well known combinatorial optimization problem, i.e., how to stabilizing the grand coalitions in unbalanced cooperative games, in the area of cooperative game theory.
We proposed a heuristic algorithm based on Lagrangian relaxation and then show its efficiency and effectiveness by implementing the heuristic algorithm on cooperative games arising in travelling salesman problems.
We hope this paper is suitable for ``Computer \& Operations Research".


We deeply appreciate your consideration of our manuscript, and we look forward to receiving comments from the reviewers. If you have any queries, please don't hesitate to contact me at the address below.
Thank you and best regards.
~\\
~\\
Yours sincerely,\\
Corresponding author: Lindong Liu\\
ldliu@ustc.edu.cn
\end{document}
